An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-11-30 paper/main.tex
add explanation for breverse and titlerunning
reduce footnote size
capitalize one

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An efficient composition of bidirectional programs
  by memoization and lazy update
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%

@@

\textcolor{red}{TODO: fix references (order, contents), add missing references}

>>>>

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
\renewcommand\UrlFont{\color{blue}\rmfamily}
\renewcommand{\footnotesize}{\scriptsize}

@@

\begin{document}
%
\title{
  % Strategies for efficient composition of bidirectional programs
  % by memoization and lazy updates
  %  tupling
  %  accumulating updates = lazy updates
  %  based on the idea of reversible computing  
  % \thanks{Supported by organization x.}  
  An Efficient Composition of Bidirectional Programs
  by Memoization and Lazy Update
}
%
\titlerunning{Strategies for efficient evaluation of BX programs}
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%

@@
